---
title: "R Notebook"
output: html_notebook
---

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
df <- read.csv(file='strategies/training_data.csv')
head(df)
```


Complete the following actions:
1) Convert position_type column to 1s and 0s
2) Convert outcome column from string to boolean
3) Drop previous index and timestamp columns 

```{r}
df$position_type <- as.integer(as.logical(df$position_type=="long"))
df$outcome <- as.logical(df$outcome=="True")
df = subset(df, select = -c(X,timestamp) )
head(df)
```

Normalize dataframe using a min-max scaler 

```{r}
min_max_scaler <- function(df)
{
    return((df- min(df)) /(max(df)-min(df)))
}

df = as.data.frame(lapply(df, min_max_scaler))
head(df)

```

Randomly shuffle rows

```{r}
df <- df[sample(nrow(df)),]
head(df)
```

Export dataset to CSV

```{r}
write.csv(df,"normalized_df.csv", row.names = FALSE)
```

split data into test and train
- 85% training data
- 15% test validation

```{r}
# set seed
set.seed(1)

# set training data to 85% of original data frame  
sample <- sample.int(n = nrow(df), size = floor(0.85*nrow(df)), replace = F)

train_data <- df[sample, ]
test_data  <- df[-sample, ]

cat("size of training data: ", nrow(train_data))
cat("\nsize of test data: ", nrow(test_data))

```


End